Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-09-06 Latex_files/Thesis/chapters/chapter 4/main.tex
updates 06/09/2024

With the initial goal of the PhD being to induce nucleation events via a 
spherical micro-rotor the goal of this chapter was to - in a limited capacity
simulate and investigate the influence of a second particle being bound to our 
target sphere. The choice of a dimer, instead of an amorphous solid that 
might better represent a growing crystalline solid, allows us to consider 
how the dynamics of the aggregate change by varying the size factor. We build 
upon the works of Vigilante \textit{et al} \cite{Vigilante2020} to consider 
asymmetric dimers and how varying size parameters alters the dynamics and 
additionally makes characterising their interactions within an optical trap 
more cumbersome. Attempting to simulate an amorphous aggregate is rather
difficult as calculating the optical force and torque is computationally 
slow and orientation specific.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Positional and Orientational dependence of Trapping forces}
\label{sec:eq_positions}
If we wanted to start from first principles and determine the trap strength 
on our target particle the first step would be to locate the equilibrium position
relative to the trap focus. For a single sphere it is easy to enough to understand 
that its centre of mass will be drawn to focal point of the laser due to gradient
forces, once there the force is analogous to a harmonic spring with a fixed trap
stiffness. Now, if we consider instead a dimer, we now have two spheres both being
drawn to the focus along by the same gradient force; in addition the scattering force
is significantly more complex due to both spheres scattering the electromagnetic 
fields. This mutual scattering between individual spheres is what makes simulating
spherical aggregates far more difficult compared to a single sphere, and even harder
still to predict the position where the dimer's centre of mass is in equilibrium.

@@

\paragraph{Simulation Parameters}
As a paradigmatic example, consider a dimer suspended in water ($n_p = 1.59, 
n_m = 1.33$) located at the focus of a Gaussian beam (more specifically a Laguerre-Gaussian beam of mode $[0,0]$), the beam is focused by a objective 
with numerical aperture of 1.2 and is x polarised. The size ratio of the two 
sphere's is given by $a_{I}/a_{II} = 2$ where $a_{I}$ is kept at $1\ \mu m$ 
unless specified otherwise; the dimer's orientation is given by a unit vector connecting the centres of both spheres, we define the 'standard' orientation 
as being aligned with the direction of beam propagation direction - and 
therefore the 'inverted' orientation is defined when the dimer is orientated 
against the direction of beam orientation (see left hand side of figure~\ref{fig:paradigmatic}).

@@

\newpage
For completeness the harmonic traps were located for dimers across a range 
of size ratios - from $a_{I}/a_{II} = 1$ to $a_{I}/a_{II}=10$ - while also 
recording the trap stiffness for each trap. The same simulation parameters are 
used here as for figures \ref{fig:paradigmatic} \& \ref{fig:transverse_force}. 
As shown in Fig.~\ref{fig:eq_positions} $a_{II}$ decrease the dimer begins to
approximate a single homogenous sphere - at least in terms of location and trap strength. However, for intermediate sized dimers (between $a_{I}/a_{II} = 1.1$ 
to $a_{I}/a_{II}=4$), a second equilibrium position is found below the trapping 
focus. Previous work using the ray-optics model have confirmed even in the case 
that two spheres begin separated the electric field will align the particles as 
such that they make contact and are trapped together about a single trapping 
position \cite{Xu2005}. Furthermore it has been shown through proper manipulation 
of the Gaussian or Bessel beam modes that any number of trapping potentials can 
be developed \cite{Shahabadi2020} for nanoparticles. This result however, is the 
first example of an orientation dependent trapping situation using only a 
$TEM_00$ beam. Typical experimental arrangements cannot determine much information 
on the axial position of a trapped particle relative to the trap focus; this 
result indicates not only that dimers can be trapped in multiple axial positions 
but also their trapping behaviour is heavily dependent on said axial position. 
As such it is necessary that positional information in the z-axis can be elucidated
if multiple spheres are trapped simultaneously.

\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.85\linewidth}
		\includegraphics[width=\linewidth]{Equillibrium_positions.png}
		\caption{}
		\label{eq_pos}
	\end{subfigure}\hfill % <-- "\hfill"
	\medskip
	\begin{subfigure}{0.85\linewidth}
		\includegraphics[width=\linewidth]{Equillibrium_positions_inverted.png}
		\caption{}
		\label{eq_pos_inverted}
	\end{subfigure}
	\caption{Equilibrium positions of optically trapped dimers with varying 
		size ratio, dashed lines represent unstable traps whereas solid lines 
		are for stable equilibrium positions. (a) shows that dimers while in their
		'standard' orientation will always have a single equilibrium position. 
		(b) shows that when the same dimer is in its' 'inverted' orientation 
		can be trapped in two axial positions, one below the focus and one above 
		the focus.}
	\label{fig:eq_positions}
\end{figure}

\newpage
\subsection{Non-trivial equilibrium configurations}
\label{sec:off-axis}
Computing the equilibrium positions when a dimer is aligned with the electric 
field is relatively simple as the orientational torque is minimised (see
Eq.\ref{eq:opt_torque}), meaning once trapped the dimer is unlikely to change
orientation enough to escape the trap. However, that does not rule out the 
possibility that there is a stable configuration where the orientation not 
strictly vertical, in fact most experimental work with symmetric nano-dimers 
will trap them lying perpendicular to the beam direction \cite{Ahn2018, 
Reimann2018}. Unlike in Sec.~\ref{sec:eq_positions} we cannot simply measure 
the optical force and torque as the parameter space is too large and determining 
if a particular position and orientation is stable is not clear based solely 
on force and torque measurements \cite{Bui2017}. Using the same simulation 
parameters as before we ran a number short simulations (total simulation time 
was $0.005$ s) with the laser power increased to $500\ mW$. Each simulation 
started with the dimer in a different starting position and orientation, due 
to the high laser power the dimers either escaped the trap or were stably 
trapped. The $z-\theta$ phase space - where $\theta$ is the angle between the 
direction of beam propagation and the dimer's orientation vector ($\theta=0^
\circ$ is the 'standard' orientation) - can be divided into different regions 
depending on which equilibrium configuration is reached.

\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.67\linewidth}
		\includegraphics[width=\linewidth]{off_axis_trap.png}
	\end{subfigure}
	\begin{subfigure}{0.32\linewidth}
		\raisebox{0pt}[0pt][0pt]{\makebox{}\includegraphics[width=\linewidth, keepaspectratio]{off_axis_render.png}}
		\caption{}
	\end{subfigure}
	%\captionsetup{hangindent=2.35cm}
	\caption{Map of $z-\theta$ phase space using a dimer of size ratio 2 with 
		a laser power of 500 mW ($\theta=0\circ$ is the 'standard' orientation 
		and $\theta=180^\circ$ is the 'inverted' orientation). The stable 
		configurations are indicated by the larger circles and the starting 
		conditions are colour coded to match the stable point they end up in. 
		Right hand render shows a dimer in its off-axis configuration.}
	\label{fig:off_axis}
\end{figure}

Interestingly while the trap strength of these off-axis traps are similar 
in magnitude to the vertically aligned dimers, but when the laser power 
is lowered (around $5\ mW$) the traps become metastable; after reaching its'
equilibrium configuration the particle behaves similarly to a typically
trapped dimer but the trapping potential is small enough that the dimer
escapes in as little time as less than a second or after nearly a full 
3 seconds. Running similar simulations but for vertical configurations 
sees the dimer remaining trapped, even after 30 seconds of run time, 
indicating that the trapping potential is far greater than the thermal 
energy. This suggests that the reason this off-axis configuration is due 
to the rotational motion more than translational motion. If the overall 
potential depth could be characterised then dimers placed into this 
orientation could be used as a micro-scale temperature alarm, where 
by fine tuning of the dimer's parameters would allow you to construct a 
potential well that can only be escaped when the local fluid temperature 
exceeds a certain maximum value.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Continuous rotational motion due to second-order scattering}

One aspect that has yet to be covered in depth with regards to spherical 
aggregates of any construction is their interaction with circularly 
polarised light. For homogenous spheres the optical torque is regarded as
being negligible as the spin density cannot impart angular momentum while 
propagating in a homogenous medium. Dimers however, have been shown to
experience an optical torque \cite{Vigilante2020, Ahn2018, Reimann2018} 
while trapped in a circular polarised beam.

First we wanted to confirm that the rotation seen in our simulations is
based on the polarisation of the trapping beam. To that end, we simulated 
the motion of an optically trapped dimer in beams of varying polarisation 
($NA=1.2$, $P=100\ mW$), the dimer is composed of polystyrene ($n_p=1.59$, 
$n_m=1.33$). Each simulation was run for $1$ second ($\Delta t =10^-5$) 
and at the end we looked at the orientational time series; the dimer's 
orientation is recorded as a quaternion which can be easily converted to 
a 3-dimensional rotation matrix. By considering only the transverse 
components ($U_{1,x}$, $U_{1,y}$, $U_{2,x}$, \& $U_{2,y}$) of the rotation 
matrix and taking the Fourier transformation of their time series reveals 
the rotational frequency. The laser power is set to $100\ mW$ to avoid 
large thermal fluctuations and so that the Fourier series of the transverse 
components approximates $\delta(\omega_{rot}-f)$ - the Dirac delta function 
centred at the rotational frequency $\omega_{rot}$.

@@

It does raise the question of how come our simulations show that despite the 
dimer being orientated so their long axis' align with the parallel to the 
direction of propagation they still readily rotate. You would not expect that
the addition of a single additional sphere should drastically adjust the torque
especially if said sphere is relatively small. However when we measured the 
optical torque of a single sphere and a dimer - $a_{I}/a_{II}=10$ - we found 
the exact opposite. In both cases we used the same trapping beam as used for
figure~\ref{fig:rotation_vs_pol} but with a circularly polarised beam. Both 
the sphere and dimer were rotated in the $x-z$ plane and the all three components 
of the optical torque were recorded.
\begin{figure}[h!]
	\centering	
	\includegraphics[width=\linewidth]{sphere_dimer_torque.png}
	\caption{Optical toque experienced by a dimer ($a_{I}/a_{II}=10$) and a 
	single isotropic sphere. Both were rotated in the $x-z$ plane and the angle 
	between $U_z$ and the beam axis gives the polar angle.The solid lines denote 
	the torque experienced by the dimer whereas the dashed lines represent the 
	torque experienced by the sphere.}
	\label{fig:sphere_dimer_torque}
\end{figure}

It should be noted that the difference in magnitude is not clearly shown in 
figure~\ref{fig:sphere_dimer_torque}. In truth, the optical torque acting on 
the dimer $10^{13}$ times greater than the torque applied to the single sphere. 
The torques about the $x$ and $y$ axis can be somewhat understood as the second 
sphere is being drawn back towards the centre of the trap by the gradient forces. 
The same cannot be said for the $z$component of the optical torque; while this 
effect could still be attributed to the spin-curl force, but it is clear that the internal scattering between the two spheres has some unintended effects.

 By repeating
the same kinds of simulation as used in \ref{fig:rotation_vs_pol} but for
a circularly polarised beam $\phi=90\circ$ it was found that not only is 
the rotation rate dependent on the size of the dimer, but also on its 
orientation and therefore their axial position.
\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{rotation_rate_vs_size.png}
  \caption{Rotation rate plotted against dimer size ratio while trapped in a
  	circularly polarised beam; a positive rotation rate indicates clockwise 
  	rotation, whereas a negative rotation rate indicates counter-clockwise 
  	rotation. The red line is for the case of a dimer in its 'standard' 
  	orientation. The blue line is for the case when the dimer is in its 
  	'inverted' orientation while trapped above the focus of the beam. And 
  	lastly the green line is for the case when the dimer is in its 
  	'inverted' orientation, but when it is trapped below the focus of the 
  	beam.}
\end{figure}

It is difficult to see from the graph, but the rotation rate never
truly goes down to zero, reaching a minimum of $2\,{\rm Hz}$, which would
imply that a second sphere of radius $200\,{\rm nm}$ is enough to
induce rotational motion. This brings into question what mechanism is
generating the optical torque. We used \textit{mstm} to look at the stokes
parameters from the scattered field from a simple plane wave incident
on a symmetric dimer, the proportion of circularly polarised light is 
minimal compared to the proportion of plane polarised light, which 
indicates that this rotational motion is not due to any inhomogeneity 
in the dimer that might impart angular momentum to the scattered beam - 
as compared to a anisotropic scatterer like vaterite. Therefore the 
rotational motion must be due to

@@

where the polarizability is given as a 3D vector for the three
principle Cartesian directions. In order to measure the magnitude of
second order contributions we would need to construct a dipole array
that fully captures the scattering of a dimer. Measuring the optical torque 
makes it clear that the polarizability is a contributing factor to this optical 
rotation phenomena. Rotating a symmetric dimer in the $x-z$ plane reveals 
that while the dimer can be rotated in an orientation perpendicular 
to the beam rotational torque is maximised when rotated while aligned with 
the optical axis.
\begin{SCfigure}
	\includegraphics[width=0.65\linewidth,height= 15cm]{torque_different_polarisations.png}
	\caption{Optical torque against polar angle $\theta$ about the three primary axis (top: torque about the x-axis; middle: torque about the y-axis; bottom: torque about the z-axis) on a symmetric dimer in linear, elliptical, and circular polarisation beams. Diagram to the right is for visual clarity about the direction of $\theta$.\vspace{4.5cm}}
\end{SCfigure}
\newpage

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
Considering the simplicity of a scatterer such as a dimer,
one would assume that the dynamics of such an object would be
relatively easy to predict. Simulations of dimers in the Mie regime
show that not only do they have multiple positions and orientations 
in which they can be trapped but also that their interaction
with circularly polarised light is heavily dependent on the axial 
position and trapping orientation. Dimer's have the potential to be used
as adaptive micro-rotors, being simple to synthesise and can be made 
out of any material of choice, but in order for these particles to be
used as such one needs a means of characterising the optical torque
applied. While estimations can be made in the Rayleigh regime due to 
the dimer being treated as point dipole, Mie regime micro rotors require 
an in-depth theoretical description of the mechanism that is creating 
this optical torque.

>>>>

With the initial goal of the PhD being to induce nucleation events via a 
spherical micro-rotor the goal of this chapter is to - in a limited capacity
simulate and investigate the influence of a second particle being bound to our 
target sphere. The choice of a dimer, instead of an amorphous solid that 
might better represent a growing crystalline solid, allows us to consider 
how the dynamics of the aggregate change by varying the size factor. 
Additionally, attempting to simulate an amorphous aggregate is rather difficult 
as calculating the optical force and torque is computationally slow. We build 
upon the works of Vigilante \textit{et al} \cite{Vigilante2020} to consider 
asymmetric dimers and how varying size parameters alters the dynamics and 
additionally makes characterising their interactions within an optical trap 
more cumbersome.

In this chapter we will consider how the addition of a second sphere changes 
the trapping dynamics by introducing multiple equilibrium positions. These 
positions are dependent on both the size ratio of the dimer and its orientation
relative to the trap. This is important to address, for while the the dimers' 
diffusive behaviour is the same, regardless of position and orientation, how it
interacts with the trap may produce the wildly different results. Furthermore,
we look at how our dimers interact with circularly polarised light, this is 
especially pertinent as the original plan was to utilise circularly polarised 
light to generate fluid flow in a supersaturated solution. The rotational motion 
of dimers in circularly polarised light goes against much of the established 
literature and suggests that the transfer of spin angular momentum is enabled 
by combining spheres together. And lastly, we demonstrate how a quadrant photo 
diode, performs in characterising the actual interactions between a dimer and 
the optical trap. We do so to demonstrate that much of the dimer's trajectory
information is either lost or poorly described by simple calibration techniques, 
making their motion difficult to characterise.

\subsection{Simulation Parameters}
As a paradigmatic example, consider a dimer suspended in water ($n_p = 1.59, 
n_m = 1.33$) located at the focus of a Gaussian beam (more specifically a 
Laguerre-Gaussian beam of mode $[0,0]$), the beam is focused by a objective 
with numerical aperture of 1.2 and is x polarised. The size ratio of the two 
sphere's is given by $a_{I}/a_{II} = 2$ where $a_{I}$ is kept at $1\ \mu m$ 
unless specified otherwise; the dimer's orientation is given by a unit vector 
connecting the centres of both spheres (see \ref{sec:sim_parameters}). We 
define the 'standard' orientation as being aligned with the direction of 
beam propagation direction - and therefore the 'inverted' orientation is 
defined when the dimer is orientated against the direction of beam 
orientation (see left hand side of figure~\ref{fig:paradigmatic}).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Positional and Orientational dependence of Trapping forces}
\label{sec:eq_positions}
If we wanted to start from first principles and determine the trap strength 
on our target particle the first step would be to locate the equilibrium position
relative to the trap focus. For a single sphere it is easy to enough to understand 
that its centre of mass will be drawn to focal point of the laser due to gradient
forces, once there the force is analogous to a harmonic spring with a fixed trap
stiffness (see fig.\ref{fig:harmonic_trap}). Now, if we consider instead a dimer, 
we now have two spheres both being drawn to the focus along by the same gradient 
force; in addition the scattering force is significantly more complex due to both 
spheres scattering the electromagnetic fields. This mutual scattering between individual 
spheres is what makes simulating spherical aggregates far more difficult compared
to a single sphere, and even harder still to predict the position where the dimer's 
centre of mass is in equilibrium.

@@

@@

\newpage
For completeness the harmonic traps were located for dimers across a range 
of size ratios - from $a_{I}/a_{II} = 1$ to $a_{I}/a_{II}=10$ - while also 
recording the trap stiffness for each trap. The same simulation parameters are 
used here as for figures \ref{fig:paradigmatic} \& \ref{fig:transverse_force}. 
As shown in Fig.~\ref{fig:eq_positions} $a_{II}$ decrease the dimer begins to
approximate a single homogenous sphere - at least in terms of location and trap strength. However, for intermediate sized dimers (between $a_{I}/a_{II} = 1.1$ 
to $a_{I}/a_{II}=4$), a second equilibrium position is found below the trapping 
focus. Previous work using the ray-optics model have confirmed even in the case 
that two spheres begin separated the electric field will align the particles as 
such that they make contact and are trapped together about a single trapping 
position \cite{Xu2005}. Furthermore it has been shown through proper manipulation 
of the Gaussian or Bessel beam modes that any number of trapping potentials can 
be developed \cite{Shahabadi2020} for nanoparticles. This result however, is the 
first example of an orientation dependent trapping situation using only a 
$TEM_00$ beam. Typical experimental arrangements cannot determine much information 
on the axial position of a trapped particle relative to the trap focus; this 
result indicates not only that dimers can be trapped in multiple axial positions 
but also their trapping behaviour is heavily dependent on said axial position. 
As such it is necessary that positional information in the z-axis can be elucidated
if multiple spheres are trapped simultaneously. 
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.85\linewidth}
		\includegraphics[width=\linewidth]{Equillibrium_positions.png}
		\caption{}
		\label{eq_pos}
	\end{subfigure}\hfill % <-- "\hfill"
	\medskip
	\begin{subfigure}{0.85\linewidth}
		\includegraphics[width=\linewidth]{Equillibrium_positions_inverted.png}
		\caption{}
		\label{eq_pos_inverted}
	\end{subfigure}
	\caption{Equilibrium positions of optically trapped dimers with varying 
		size ratio, dashed lines represent unstable traps whereas solid lines 
		are for stable equilibrium positions. (a) shows that dimers while in their
		'standard' orientation will always have a single equilibrium position. 
		(b) shows that when the same dimer is in its' 'inverted' orientation 
		can be trapped in two axial positions, one below the focus and one above 
		the focus.}
	\label{fig:eq_positions}
\end{figure}

\newpage
\subsection{Non-trivial equilibrium configurations}
\label{sec:off-axis}
Computing the equilibrium positions when a dimer is aligned with the electric 
field is relatively simple as the orientational torque is minimised (see
Eq.\ref{eq:opt_torque}). Meaning once trapped the dimer is unlikely to change
orientation enough to escape the trap. Regardless, that does not rule out the 
possibility that there is a stable configuration where the orientation not 
strictly vertical, in fact most experimental work with symmetric nano-dimers 
will trap them lying perpendicular to the beam direction \cite{Ahn2018, 
Reimann2018}. Unlike in Sec.~\ref{sec:eq_positions} we cannot simply measure 
the optical force and torque as the parameter space is too large and determining 
if a particular position and orientation is stable is not clear based solely 
on force and torque measurements \cite{Bui2017}. Using the same simulation 
parameters as before we ran a number short simulations (total simulation time 
was $0.005$ s) with the laser power increased to $500\ mW$. Each simulation 
started with the dimer in a different starting position and orientation, due 
to the high laser power the dimers either escaped the trap or were stably 
trapped. The $z-\theta$ phase space - where $\theta$ is the angle between the 
direction of beam propagation and the dimer's orientation vector ($\theta=0^
\circ$ is the 'standard' orientation) - can be divided into different regions 
depending on which equilibrium configuration is reached.
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.67\linewidth}
		\includegraphics[width=\linewidth]{off_axis_trap.png}
	\end{subfigure}
	\begin{subfigure}{0.32\linewidth}
		\raisebox{0pt}[0pt][0pt]{\makebox{}\includegraphics[width=\linewidth, keepaspectratio]{off_axis_render.png}}
		\caption{}
	\end{subfigure}
	%\captionsetup{hangindent=2.35cm}
	\caption{Map of $z-\theta$ phase space using a dimer of size ratio 2 with 
		a laser power of 500 mW ($\theta=0\circ$ is the 'standard' orientation 
		and $\theta=180^\circ$ is the 'inverted' orientation). The stable 
		configurations are indicated by the larger circles and the starting 
		conditions are colour coded to match the stable point they end up in. 
		Right hand render shows a dimer in its off-axis configuration.}
	\label{fig:off_axis}
\end{figure}

Interestingly while the trap strength of these off-axis traps are similar 
in magnitude to the vertically aligned dimers, but when the laser power 
is lowered (around $5\ mW$) the traps become metastable; after reaching its'
equilibrium configuration the particle behaves similarly to a typically
trapped dimer but the trapping potential is small enough that the dimer
escapes in as little time as less than a second or after nearly a full 
3 seconds. Running similar simulations but for vertical configurations 
sees the dimer remaining trapped, even after 30 seconds of run time, 
indicating that the trapping potential is far greater than the thermal 
energy. This suggests that the reason this off-axis configuration is 
metastable is due to the increased rotational freedom. Similar 
configurations have been explored with ellipsoids; Zhu \textit{et al.} 
looked at the dynamics of various elliptical particles and found that 
regardless of shape or initial orientation the particle would tend towards
either a purely vertical or purely horizontal orientation \cite{Zhu2021}. 
It highlights an interesting aspect of the dimer's behaviour, namely that 
the potential phase space $U(\textbf{r}, \theta, \phi)$ is not continuous.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Continuous rotational motion due to second-order scattering}
One aspect that has yet to be covered in depth with regards to spherical 
aggregates of any construction is their interaction with circularly 
polarised light. For homogenous spheres the optical torque is regarded as
being negligible as the spin density cannot impart angular momentum while 
propagating in a homogenous medium. Dimers however, have been shown to
experience an optical torque \cite{Vigilante2020, Ahn2018, Reimann2018} 
while trapped in a circular polarised beam. In our simulations we found 
that dimers would rotate about their long axis when trapped in circularly
polarised light. In this section we want to discuss how this behaviour 
is influenced by size, position, and orientation; and furthermore, we wish
to address possible explanations for this behaviour, as none of the current
theories into optically induced rotation seem plausible.

\subsection{Polarisation Dependency on Dimer trajectory}
First we wanted to confirm that the rotation seen in our simulations is
based on the polarisation of the trapping beam. To that end, we simulated 
the motion of an optically trapped dimer in beams of varying polarisation 
($NA=1.2$, $P=100\ mW$), the dimer is composed of polystyrene ($n_p=1.59$, 
$n_m=1.33$). Each simulation was run for $1$ second ($\Delta t =10^-5$) 
and at the end we looked at the orientational time series; the dimer's 
orientation is recorded as a quaternion which can be easily converted to 
a 3-dimensional rotation matrix. By considering only the transverse 
components ($U_{1,x}$, $U_{1,y}$, $U_{2,x}$, \& $U_{2,y}$) of the rotation 
matrix and taking the Fourier transformation of their time series reveals 
the rotational frequency. The laser power is set to $100\ mW$ to avoid 
large thermal fluctuations and so that the Fourier series of the transverse 
components approximates $\delta(\omega_{rot}-f)$ - the Dirac delta function 
centred at the rotational frequency $\omega_{rot}$.

@@

\subsection{Comparison of optical torques for Sphere and Dimers}
It does raise the question of how come our simulations show that despite the 
dimer being orientated so their long axis' align with the parallel to the 
direction of propagation they still readily rotate. You would not expect that
the addition of a single additional sphere should drastically adjust the torque
especially if said sphere is relatively small. However when we measured the 
optical torque of a single sphere and a dimer - $a_{I}/a_{II}=10$ - we found 
the exact opposite. In both cases we used the same trapping beam as used for
figure~\ref{fig:rotation_vs_pol} but with a circularly polarised beam. Both 
the sphere and dimer were rotated in the $x-z$ plane and the all three components of the optical torque were recorded.
\begin{figure}[h!]
	\centering	
	\includegraphics[width=\linewidth]{sphere_dimer_torque.png}
	\caption{Optical toque experienced by a dimer ($a_{I}/a_{II}=10$) and a 
	single isotropic sphere. Both were rotated in the $x-z$ plane and the angle 
	between $U_z$ and the beam axis gives the polar angle.The solid lines denote 
	the torque experienced by the dimer whereas the dashed lines represent the 
	torque experienced by the sphere.}
	\label{fig:sphere_dimer_torque}
\end{figure}

The torques about the $x$ and $y$ axis can be somewhat understood as the second 
sphere is being drawn back towards the centre of the trap by the gradient forces. The same cannot be said for the $z$component of the optical torque; while this effect could still be attributed to the spin-curl force, but it is clear that the internal scattering between the two spheres has some unintended effects.

\subsection{Rotational frequency as a function of size ratio and orientation}
Moving on, next we want to see how the rotational speed is influenced by 
different sized dimers. Intuitively, you would expect that a larger would 
experience a greater torque and therefore rotate faster. By repeating the same kinds of simulation as used in \ref{fig:rotation_vs_pol} but for a circularly polarised beam $\phi=90\circ$ it was found that not only is the rotation rate dependent on the size of the dimer, but also on its orientation and therefore their axial position.
\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{rotation_rate_vs_size.png}
  \caption{Rotation rate plotted against dimer size ratio while trapped in a
  	circularly polarised beam; a positive rotation rate indicates clockwise 
  	rotation, whereas a negative rotation rate indicates counter-clockwise 
  	rotation. The red line is for the case of a dimer in its 'standard' 
  	orientation. The blue line is for the case when the dimer is in its 
  	'inverted' orientation while trapped above the focus of the beam. And 
  	lastly the green line is for the case when the dimer is in its 
  	'inverted' orientation, but when it is trapped below the focus of the 
  	beam.}
\end{figure}

It is difficult to see from the graph, but the rotation rate never
truly goes down to zero, reaching a minimum of $2\,{\rm Hz}$, which would
imply that a second sphere of radius $200\,{\rm nm}$ is enough to
induce rotational motion. This brings into question what mechanism is
generating the optical torque. We used \textit{mstm} to look at the stokes
parameters from the scattered field from a simple plane wave incident
on a symmetric dimer, the proportion of circularly polarised light is 
minimal compared to the proportion of plane polarised light, which 
indicates that this rotational motion is not due to any inhomogeneity 
in the dimer that might impart angular momentum to the scattered beam - 
as compared to a anisotropic scatterer like vaterite.

@@

where the polarizability is given as a 3D vector for the three
principle Cartesian directions. In order to measure the magnitude of
second order contributions we would need to construct a dipole array
that fully captures the scattering of a dimer. Measuring the optical torque 
makes it clear that the polarizability is a contributing factor to this optical 
rotation phenomena.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
Considering the simplicity of a scatterer such as a dimer,
one would assume that the dynamics of such an object would be
relatively easy to predict. Simulations of dimers in the Mie regime
show that not only do they have multiple positions and orientations 
in which they can be trapped but also that their interaction
with circularly polarised light is heavily dependent on the axial 
position and trapping orientation. Dimer's have the potential to be used
as adaptive micro-rotors, being simple to synthesise and can be made 
out of any material of choice, but in order for these particles to be
used as such one needs a means of characterising the optical torque
applied. While estimations can be made in the Rayleigh regime due to 
the dimer being treated as point dipole, Mie regime micro rotors require 
an in-depth theoretical description of the mechanism that is creating 
this optical torque.
